API design for machine learning software: experiences from the scikit-learn project

### 2013-06-28 paper.tex
off-topic -> out of scope (@ogrisel + @amueller)

\section{Future directions}
\label{sec:future_work}
There are several directions that the \sklearn project
aims to focus on in future development.
At present, the library does not support some classical machine learning
algorithms,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
However, tasks like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

>>>>

\section{Future directions}
\label{sec:future_work}
There are several directions that the \sklearn project
aims to focus on in future development.
At present, the library does not support some classical machine learning
algorithms,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
However, tasks like structured prediction or reinforcement learning are
considered out of scope for the project,
since they would require quite different data representations and APIs.
